%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {Research Center for Information Technology Innovation, Academia Sinica} % Organization
    {Taipei, Taiwan, R.O.C} % Location
    {Sept. 2022 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Build and test robust model for generalizable facial video forgery (Deepfake) detection.}
        \item {Explore the frontier of generative and discriminative models in the field of computer vision.}
        \item {Study novel approaches to improve autonomous driving.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Full-Stack Web Developer (Part-Time)} % Job title
    {Office of International Affairs, NSYSU} % Organization
    {Kaohsiung, Taiwan, R.O.C} % Location
    {Sept. 2018 - June 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain the application system for exchange program using PHP, Nginx and MariaDB.}
        \item {Design and build the exchange program platform from scratch using Vue.js, Express.js, Sequelize.js and MariaDB.}
        \item {Maintain the official website for each division incorporating with Rpage, HeimaVista, Inc.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Data Engineer Intern} % Job title
    {Northwest Analytics Inc - Taiwan} % Organization
    {Kaohsiung, Taiwan, R.O.C} % Location
    {June 2018 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data preprocessing for factory monitoring.}
        \item {Foundational Industry 4.0 Analytics.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
