%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  % \cventry
  %   {Researcher} % Role
  %   {Wafer Map Defect Pattern Classification} % Title
  %   {NSYSU, Taiwan, R.O.C} % Location
  %   {June. 2022 - Present} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s)
  %       \item {Compare the effectiveness between convolution-based and self-attention-based models.}
  %       \item {Self-supervised model pre-training on unlabeled wafer map defect patterns to boost the performance.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Leading Developer} % Role
    {LoLViZ.} % Title
    {NSYSU, Taiwan, R.O.C} % Location
    {May. 2022 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {A League of Legends visualizer that helps the pro players in the challenger league exploring their matches.}
        \item {Use Vue.js along with D3.js to create flexible and meaningful visualizations.}
        \item {Utilize the Riot API and AWS cloud services to retrieve the latest player and match informations.}
        \item {\textbf{Demo}: \href{https://www.ernestchu.org/lol-viz/}{https://www.ernestchu.org/lol-viz/}}
        \item {\textbf{Talk}: \href{https://youtu.be/hQ1XeHcu0ns}{https://youtu.be/hQ1XeHcu0ns}}
        \item {\textbf{Repository}: \href{https://github.com/ernestchu/lol-viz}{https://github.com/ernestchu/lol-viz}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer, Researcher \& Co-Author} % Role
    {TSM-Net: Audio Time-Scale Modification with Temporal Compressing Networks} % Title
    {NSYSU, Taiwan, R.O.C} % Location
    {Jan. 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Use an autoencoder to compress the audio into 1024 times smaller latent representation for time-scale modification.}
        \item {Use multi-scale discriminator to train the model for the best audio quality on all frequency bands.}
        \item {\textbf{Demo}: \href{https://ernestchu.github.io/tsm-net-demo/}{https://ernestchu.github.io/tsm-net-demo/}}
        \item {\textbf{Paper}: \href{https://arxiv.org/abs/2210.17152}{https://arxiv.org/abs/2210.17152}}
        \item {\textbf{Poster}: \href{https://ernestchu.github.io/tsm-net-poster/poster.pdf}{https://ernestchu.github.io/tsm-net-poster/poster.pdf}}
        \item {\textbf{Talk}: \href{https://youtu.be/h69v7\_ZOKCM}{https://youtu.be/h69v7\_ZOKCM}}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Leading Developer} % Affiliation/role
    {NSYSU Captcha Solver} % Organization/group
    {NSYSU, Taiwan, R.O.C} % Location
    {Jan. 2021 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Use convolutional neural networks to autofill the captcha verification in the course explorer.}
        \item {Use TensorFlow.js in Chrome extension to implement on-device inference.}
        \item {\textbf{Repository}: \href{https://github.com/ernestchu/nsysu-captcha-solver}{https://github.com/ernestchu/nsysu-captcha-solver}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer \& Co-Author} % Affiliation/role
    {Secure On-line Chatting Service} % Organization/group
    {NSYSU, Taiwan, R.O.C} % Location
    {Spring 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {On-line chatting service with console-based UI using ncurses.}
        \item {Socket programming and multi-threading using C++17}
        \item {Use attribute-based encryption to provide secure channel for messages.}
        \item {\textbf{Demo}: \href{https://youtu.be/S-j5kQz\_-7Y}{https://youtu.be/S-j5kQz\_-7Y}.}
        \item {\textbf{Paper}: \href{https://ernestchu.github.io/abe-examples/paper.pdf}{https://ernestchu.github.io/abe-examples/paper.pdf}.}
        \item {\textbf{Repository}: \href{https://github.com/ernestchu/on-line-chatting-service/tree/abe}{https://github.com/ernestchu/on-line-chatting-service/tree/abe}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Leading Developer} % Affiliation/role
    {License Plate Verification System} % Organization/group
    {NSYSU, Taiwan, R.O.C} % Location
    {Fall 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Use ML-based object detection technology to track the license plate.}
        \item {No parking barrier is required since our system can detect moving target.}
        \item {All of the inferences can be done on edge-device, for example Jetson Nano.}
        \item {\textbf{Demo}: \href{https://youtu.be/jDKGAp2Puh0}{https://youtu.be/jDKGAp2Puh0}.}
        \item {\textbf{Repository}: \href{https://github.com/ernestchu/license-plate-verification-warning-system}{https://github.com/ernestchu/license-plate-verification-warning-system}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer, Researcher \& Co-Author} % Affiliation/role
    {Deep Generative Models For ECG Denoising And Filtering} % Organization/group
    {NSYSU, Taiwan, R.O.C} % Location
    {Fall 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Utilize domain-transferring generative models to mitigate the noise within ECG signals.}
        \item {This work deals with the classification of realistic noisy data and provides pragmatic results.}
        \item {\textbf{Paper}: \href{https://ernestchu.github.io/noise-ecg-classification/paper.pdf}{https://ernestchu.github.io/noise-ecg-classification/paper.pdf}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

