\cvsection{Publications \& Preprints}

\descriptionstyle{
\begin{enumerate}[label={[\arabic*]}]
\item Po-Han Huang, Yue-Hua Han, \textbf{Ernie Chu}, Jun-Cheng Chen, and Kai-Lung Hua. \textbf{Multi-Task Self-Blended Images for Face Forgery Detection.} \textit{ACM Multimedia Asia}, 2023.
\item \textbf{Ernie Chu}, Tzuhsuan Huang, Shuo-Yen Lin, and Jun-Cheng Chen. \textbf{MeDM: Mediating Image Diffusion Models for Video-to-Video Translation with Temporal Correspondence Guidance.} \textit{arXiv preprint arXiv:2308.10079}, 2023. \hspace*{\fill} \href{https://medm2023.github.io}{\faDesktop} \href{https://arxiv.org/abs/2308.10079}{\faFilePdfO} \href{https://github.com/aiiu-lab/MeDM}{\faGithub}
\item \textbf{Ernie Chu}, Shuo-Yen Lin, and Jun-Cheng Chen. \textbf{Video ControlNet: Towards Temporally Consistent Synthetic-to-Real Video Translation Using Conditional Image Diffusion Models.} \textit{arXiv preprint arXiv:2305.19193}, 2023. \hspace*{\fill} \href{https://arxiv.org/abs/2305.19193}{\faFilePdfO}
\item Shuo-Yen Lin, \textbf{Ernie Chu}, Che-Hsien Lin, Jun-Cheng Chen, and Jia-Ching Wang. \textbf{Diffusion to Confusion: Naturalistic Adversarial Patch Generation Based on Diffusion Model for Object Detector.} \textit{arXiv preprint arXiv:2307.08076}, 2023. \hspace*{\fill} \href{https://arxiv.org/abs/2307.08076}{\faFilePdfO} 
\item \textbf{Ernie Chu}, Ju-Ting Chen, and Chia-Ping Chen. \textbf{Audio Time-Scale Modification with Temporal Compressing Networks.} \textit{arXiv preprint arXiv:2210.17152}, 2022. \hspace*{\fill} \href{https://tsmnet-mmasia23.github.io}{\faDesktop} \href{https://arxiv.org/abs/2210.17152}{\faFilePdfO} \href{https://github.com/tsmnet-mmasia23/tsmnet}{\faGithub}
\end{enumerate}
}

